V1298~Tau with TESS: Updated Ephemerides, Radii, and Period Constraints for a Previous Single Transit Event of V1298~Tau~e

### 2021-11-01 src/ms.tex
updates

\author[0000-0002-3199-2888]{Sarah Blunt}
\altaffiliation{NSF Graduate Research Fellow}
\affiliation{Department of Astronomy, California Institute of Technology, Pasadena, CA, USA}

@@

%%%%%%%%%%%%%%%%%%%%
% abstract must be < 250 words
% currently at 180 words
%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\sname is a young (20--30~Myr) solar analogue hosting four transiting exoplanets with sizes between $0.5 - 0.9 R_J$. Given the system's youth,  it provides a unique opportunity to understand the evolution of planetary radii in the same stellar environment. \sname was originally observed 6 years ago during K2 Campaign 4. The extended mission of NASA's Transiting Exoplanet Survey Satellite (\tess) includes observing the ecliptic plane. Here, we present new photometric observations of \sname from the 10-minute TESS Full-Frame Images. We use the TESS data to update the transit-timing for \allplanets as well as compare newly observed radii to those derived from the K2 light curve, finding shallower transits in the redder \tess\ bandpass at the $1-2\sigma$ level. We hypothesize the shallower transits observed by \tess\ may be due to high-altitude hazes in the extended atmospheres of these young planets. We additionally catch a transit of \planete, which was only observed once during the \textit{K2} observations, and present a novel method for deriving the marginalized posterior probability of a planet from two transits observed years apart. We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, would make this a nearly 4 planet resonant chain. \sname is the target of several ongoing and future observations, including with the James Webb Space Telescope. These updated ephemerides will be crucial for accurately recovering transit events and understanding any future Doppler tomographic or transmission spectroscopy signals.\end{abstract}

@@

\section{Introduction} \label{sec:intro}
Planetary sizes are expected to evolve over time, due to a variety of endogenous and exogenous physical processes including gravitational contraction, atmospheric heating and mass-loss, and core-envelope interactions \citep[e.g.][]{OwenWu2013, Lopez2013, Jin2014, ChenRogers2016, Ginzburg2018}. Dramatic size evolution is expected at early stages, when planets are still contracting and radiating away the energy from their formation, and when host stars are heating planetary atmospheres with high levels of X-ray and ultraviolet radiation. Since the size evolution of any individual planet is believed to be slow relative to typical observational baselines, the best way to make inferences about the size evolution of exoplanets is by measuring the sizes of large numbers of planets across a range of ages.

NASA's Transiting Exoplanet Survey Satellite \citep[TESS,][]{Ricker2015} has made significant inroads toward this objective. \tess's observations of $\sim 90 \%$ of the sky have allowed for exoplanet transit searches around stars ranging from the pre-main sequence to the giant branch. It is through targeted surveys of young stars such as the THYME \citep[e.g.][]{Newton2019}, PATHOS \citep[e.g.][]{Nardiello2020}, and CDIPS \citep[e.g.][]{Bouma2020} surveys, along with case studies of individual systems \citep[e.g.][]{benatti19, Plavchan2020, Hedges2021, Zhou2021} that the timeline for planetary radius evolution can be pieced together.

The \sname planetary system is one particularly valuable benchmark for understanding the size evolution of exoplanets. \sname is a pre-main sequence, approximately solar-mass star that was observed in 2015 by NASA's \textit{K2} mission \citep{Howell2014}. Analysis of the \textit{K2} data revealed the presence of four transiting planets, all with sizes between the sizes of Neptune and Jupiter \citep{David2019a, David2019b}. There are no other known examples of exoplanetary systems with so many planets larger than Neptune interior to 0.5~au, despite the high completeness of the Kepler survey to large ($>5$~\rearth), close-in planets. This observation raises the possibility of a causal connection between the extreme youth of \sname and the uncommonly large sizes of its planets.

@@

Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems \citep[e.g.][]{Poppenhaeger2021, Owen2020}, \sname has been the target for extensive follow-up observations. These include efforts to constrain planet masses with radial velocities \citep{Beichman2019}, measure the spin-orbit alignments of planet c \citep{Feinstein21} and planet b (Johnson et al. submitted; Gaidos et al. submitted), measure or constrain atmospheric mass-loss rates for the innermost planets \citep{Schlawin21, Vissapragada21}, and an approved program to study the planetary atmospheres using the James Webb Space Telescope \citep{Desert2021}.

Here we report on newly acquired TESS observations of \sname which help to refine the orbital ephemerides of the transiting planets and enable comparison of the planet sizes inferred from two different telescopes with different bandpasses (\tess\ and Kepler). We describe the observations and light curve extraction in Section~\ref{sec:observations}. In Section~\ref{sec:analysis}, we present our transit and stellar variability modeling. We additionally present a novel method for computing the marginalized posterior probability of a transiting planet's period from two transits observed with a large gap between them. We discuss the differences in measured transit parameters between \textit{K2} and \tess\ data. We conclude in Section~\ref{sec:conclusions}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
\caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band. \sname is shown in the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with orange x's. There are two bight nearby sources to \sname. However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible. \href{https://github.com/afeinstein20/v1298tau_tess/blob/main/src/figures/tpf.py}{\github}} \label{fig:tpf}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We created light curves from the \texttt{tica}-processed FFIs by modeling the point-spread function (PSF) of \sname and the two nearby bright sources (see Figure~\ref{fig:tpf}), following the PSF modeling routine in \cite{feinstein19}. In summary, we calculated and maximized the likelihood value of four parameters per each Gaussian: the $x$ and $y$ width, amplitude, and a rotational term. The Gaussian fits are allowed to vary at each time step. While aperture photometry provided a decent light curve, we found that modeling each star (3 in total) with a 2D Gaussian created a less contaminated light curve for \sname. Our extracted light curve is shown in the top row of Figure~\ref{fig:transits}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hbtp]
\begin{center}
\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
\caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images for all of Sector 43 and the first orbit of Sector 44, with transits of \allplanets highlighted by color. Each subplot contains the raw, normalized \tess\ flux (top) and the GP model removed flux (de-trended flux; bottom). Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (black). Bottom three rows: zoomed-in regions around the transits present in the \tess\ data. The GP best-fit model is over-plotted on the raw, normalized flux. The best-fit transit models are over-plotted on the de-trended flux. For overlapping transits, the sum of the transits is blotted in black.} \label{fig:transits}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We took a two-step approach to modeling any background contamination. First, we defined a quadratic trend with respect to time for varying the background flux, where each term was drawn from a normal distribution (listed as `trend term' in Table~\ref{tab:table}). Then, we generated a Vandermonde matrix ($A$) of time. This is a way of introducing a polynomial least-squares regression with respect to time. The final background flux was calculated by taking $bkg = A \cdot trend$.  
We performed an MCMC sampling fit to each parameter. We ran 3 chains with 500 tuning steps and 2000 draws. We discarded the tuning samples in our final modeling best-fits, presented in Table~\ref{tab:table}. We verified our chains converged via visual inspection and following the diagnostic provided by \cite{Geweke92}.

Our final GP model for stellar variability and planet transits are shown in Figure~\ref{fig:transits}. There is a $\sim 1\%$ flare at \tess\ BJD 4659.18 that we do not fit. Zoom-ins on the individual transits that occur are presented in the bottom two rows of Figure~\ref{fig:transits}. Phase-folded transits for \planetc and \planetd are presented in Figure~\ref{fig:compare}.

@@

For this analysis, we created a GP model that constrains the period of \planete by sampling over discrete periods, ranging from $38 - 56$~days. We fit for the additional transit parameters, $\theta$, assuming a constant transit depth between the \textit{K2} and \tess\ observations, $X$. To speed up the computation of the GP fits, we localized a 1-day window around each transit of \planete.

We assumed there is no correlation between the other transit parameters and the period we are fitting for. For each step in our MCMC fit, we compute all possible periods

@@

We chose to test periods from $38-56$~days. We ran 5 chains with 500 tuning steps and 5000 draws. Similarly to the transit fits, we discarded the tuning steps before our analysis. We show our results in Figure~\ref{fig:period_e}, where we plot the median period for each tested harmonic against the posterior probability of each harmonic.

@@

Using this method, we find the most likely period of \planete to be 50.748~days. We computed a $\chi^2$-fit to a Gaussian distribution and find the period to be $50.29 \pm 6.62$~days. Even at the lower limit, it is unlikely a transit of \planete will occur in the next sector (Sector 44) of \tess\ data for \sname. However, this derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb.

Independent ground-based monitoring of the system for several days beyond the end of Sector 44 (UT 06 Nov 2021) may be able to observe another transit of the outermost known planet in this system. We provide several transit dates and times that are observable from Mauna Kea, given the top 5 most-likely periods of \planete, in Table~\ref{tab:planete}

@@

We compare the differences in transit $R_p/R_\star$ between the \textit{K2} and \tess\ data in Figure~\ref{fig:compare}. We plot the best-fit transit model from \textit{K2} in black, which was generated using parameters from \cite{David2019a} and the \texttt{batman} transit-modeling software \citep{Kreidberg15}. The residuals of the \tess\ light curve with our model and the \textit{K2} model are plotted as well. For each planet, the transit $R_p/R_\star$ is shallower in the \tess\ data (Figure~\ref{fig:compare}, bottom panel).

Because \sname is young, it is expected that \allplanets have extended atmospheres due to high levels of stellar irradiation \citep{OwenWu2017} and are slowly evolving as atmospheric mass is lost. Only a tentative mass-loss rate of \planetd has been constrained from observations of the metastable He\textsc{I} line, along with non-detections for \planetb and \planetc \citep{Vissapragada21}. As such, we favor that the shallower transit depth is due to the difference in bandpass wavelength coverage between \textit{K2} and \tess, rather than atmospheric evolution. The \textit{K2} bandpass ranges from $\sim 400-900$~nm \citep{Howell2014}, while the \tess\ bandpass ranges from $\sim 600-1000$~nm \citep{Ricker2015}. A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.465\textwidth,trim={0.25cm 0 4.5cm 0}]{figures/folded_compare.pdf}
\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black). The residuals between the data and each fit are shown underneath. A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference. The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.} \label{fig:compare}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The ability of a planet to retain hazes/transition hazes is positively correlated with its equilibrium temperature, $T_{eq}$, internal temperature $T_{int}$, and mass, $M_{core}$. \allplanets have calculated $T_{eq}<1000$\,K, assuming an albedo = 0 \citep{David2019a}. Young planets are believed to have high $T_{int}$ due to ongoing gravitational contraction \citep{gu04}. The combination of these two parameters make these planets more likely to have extended atmospheres, while outflow winds lead to the formation of transition hazes \citep{gao20}.

If \allplanets host extended haze-dominated atmospheres, they should have smaller transit radii at mid-IR wavelengths \citep{gao20}. However, without mass estimates for \allplanets, it is difficult to determine if this is the cause of the different transit depths we measured between the \textit{K2} and \tess\ data. While radial velocity mass measurements are challenging for young planets due to the underlying stellar activity, efforts should be taken to try and constrain the planet masses.

Another, perhaps more promising approach, would be to derive the planet masses using transit-timing variations \citep[TTVs;][]{agol18}. A full TTV analysis using \textit{K2}, \textit{Spitzer}, and \tess\ transit photometry is presented in Livingston et al. (in prep).

@@

We find the transit depths of \allplanets as observed by \tess\ are shallower than previous \textit{K2} by $1-2\sigma$. We postulate this could be due to ongoing dusty outflows, that make the transit depth appear shallower. However, measuring the transit depths at longer wavelengths could corroborate this.

@@

\begin{acknowledgments}
We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter and Chas Beichman for helpful comments on our \tess\ DDT proposal 36. It is a pleasure to thank the Astronomical Data Group at the Flatiron Institute for helpful discussions. ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No. (DGE-1746045).

@@

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

>>>>

%\author[0000-0002-3199-2888]{Sarah Blunt}
%\altaffiliation{NSF Graduate Research Fellow}
%\affiliation{Department of Astronomy, California Institute of Technology, Pasadena, CA, USA}

%\author[0000-0003-3654-1602]{Andrew~W.~Mann}
%\affiliation{1Department of Physics and Astronomy, The University of North Carolina at Chapel Hill, Chapel Hill, NC 27599, USA}

@@

%%%%%%%%%%%%%%%%%%%%
% abstract must be < 250 words
% currently at 180 words
%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

\sname is a young (20--30~Myr) solar analogue hosting four transiting exoplanets with sizes between $0.5 - 0.9 R_J$. Given the system's youth,  it provides a unique opportunity to understand the evolution of planetary radii at different separations in the same stellar environment. \sname was originally observed 6 years ago during \textit{K2} Campaign 4. Now, \sname has been re-observed during the extended mission of NASA's Transiting Exoplanet Survey Satellite (\tess). Here, we present new photometric observations of \sname from the 10-minute \tess\ Full-Frame Images. We use the \tess\ data to update the transit-timing for \allplanets as well as compare newly observed radii to those derived from the \textit{K2} light curve, finding shallower transits for \planetknown in the redder \tess\ bandpass at the $1-2\sigma$ level. We hypothesize the shallower transits observed by \tess\ may be due to high-altitude hazes in the extended atmospheres of these young planets. We additionally catch a transit of \planete, which was only observed once during the \textit{K2} observations, and present a novel method for deriving the marginalized posterior probability of a planet's period from two transits observed years apart. We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, would make \allplanets a nearly 4 planet resonant chain. Additionally, we find the transit depth to be deeper for \planete, than what was originally measured from \textit{K2}. \sname is the target of several ongoing and future observations, including with the James Webb Space Telescope. These updated ephemerides will be crucial for accurately recovering transit events and understanding any future Doppler tomographic or transmission spectroscopy signals.

\end{abstract}

@@

\section{Introduction} \label{sec:intro}
Planetary radii are expected to evolve over time, due to a variety of endogenous and exogenous physical processes, such as gravitational contraction, atmospheric heating and mass-loss, and core-envelope interactions \citep[e.g.][]{OwenWu2013, Lopez2013, Jin2014, ChenRogers2016, Ginzburg2018}. The most dramatic changes are believed to occur at early stages, when planets are still contracting and radiating away the energy from their formation, and when host stars are heating planetary atmospheres with high levels of X-ray and ultraviolet radiation. Since the size evolution of any individual planet is believed to be slow relative to typical observational baselines, the best way to make inferences about the size evolution of exoplanets is by measuring the sizes of large numbers of planets across a range of ages.

NASA's Transiting Exoplanet Survey Satellite \citep[\tess;][]{Ricker2015} has made significant inroads toward this objective. \tess's observations of $\sim 90 \%$ of the sky have allowed for exoplanet transit searches around stars ranging from the pre-main sequence to the giant branch. It is through targeted surveys of young stars such as the THYME \citep[e.g.][]{Newton2019}, PATHOS \citep[e.g.][]{Nardiello2020}, and CDIPS \citep[e.g.][]{Bouma2020} surveys, along with case studies of individual systems \citep[e.g.][]{benatti19, Plavchan2020, Hedges2021, Zhou2021} that the timeline for planetary radii evolution can be pieced together.

The \sname planetary system is one particularly valuable benchmark for understanding the size evolution of exoplanets. \sname is a pre-main sequence, approximately solar-mass star that was observed in 2015 by NASA's \textit{K2} mission \citep{Howell2014}. Analysis of the \textit{K2} data revealed the presence of four transiting planets, all with sizes between that of Neptune and Jupiter \citep{David2019a, David2019b}. There are no other known examples of exoplanetary systems with so many planets larger than Neptune interior to 0.5~au, despite the high completeness of the \textit{Kepler} survey to large ($>5$~\rearth), close-in planets. This observation raises the possibility of a causal connection between the extreme youth of \sname and the uncommonly large sizes of its planets.

@@

Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems \citep[e.g.][]{Poppenhaeger2021, Owen2020}, \sname has been the target for extensive follow-up observations. These include efforts to constrain planet masses with radial velocities \citep{Beichman2019}, measure the spin-orbit alignments of planet c \citep{Feinstein21} and planet b \citep{johnson21, gaidos21}, measure or constrain atmospheric mass-loss rates for the innermost planets \citep{Schlawin21, Vissapragada21}, and an approved program to study the planetary atmospheres using the James Webb Space Telescope \citep{Desert2021}.

Here we report on newly acquired \tess\ observations of \sname which help to refine the orbital ephemerides of the transiting planets and enable comparison of the planet sizes inferred from two different telescopes with different bandpasses (\tess\ and \textit{Kepler}). The letter is laid out as follows. We describe the observations and light curve extraction in Section~\ref{sec:observations}. In Section~\ref{sec:analysis}, we present our transit and stellar variability modeling. We additionally present a novel method for computing the marginalized posterior probability of a transiting planet's period from two transits observed with a large gap between them. We provide transit mid-point dates and times for \planete for ground-based follow-up in the United States. In Section~\ref{sec:radii}, we discuss the differences in measured transit parameters between \textit{K2} and \tess\ data and speculate on the causes for different measured radii. We conclude in Section~\ref{sec:conclusions}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
\caption{The \tess\ \texttt{tica} FFI target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band. \sname highlighted by the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with orange x's. There are two bight nearby sources to \sname. While aperture photometry would be feasible for this system (yellow square), we found fitting three point-spread functions to the brightest stars extracted the cleanest light curve for \sname. \href{https://github.com/afeinstein20/v1298tau_tess/blob/main/src/figures/tpf.py}{\github}} \label{fig:tpf}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We created light curves from the \texttt{tica}-processed FFIs by modeling the point-spread function (PSF) of \sname and the two nearby bright sources (see Figure~\ref{fig:tpf}), following the PSF modeling routine in \cite{feinstein19}. In summary, we calculated and maximized the likelihood value of four parameters per each Gaussian: the $x$ and $y$ width, amplitude, and a rotational term. The Gaussian fits are allowed to vary at each time step. While aperture photometry (example aperture shown in Figure~\ref{fig:tpf}) provided a decent light curve, we found that modeling each star (3 in total) with a 2D Gaussian created a less contaminated light curve for \sname. Our extracted light curve is shown in the top row of Figure~\ref{fig:transits}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hbtp]
\begin{center}
\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
\caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images for all of Sector 43 and the first orbit of Sector 44, with transits of \allplanets highlighted by color. Each subplot contains the raw, normalized \tess\ flux (top) and the GP model removed flux (de-trended flux; bottom). Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (black). Bottom three rows: zoomed-in regions around the transits present in the \tess\ data. The GP best-fit model is over-plotted on the raw, normalized flux. The best-fit transit models are over-plotted on the de-trended flux. For overlapping transits (sub-panel `Planets b, c, \& e`), the sum of the transits is blotted in black.} \label{fig:transits}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We took a two-step approach to modeling any background contamination. First, we defined a quadratic trend with respect to time for varying the background flux, where each term was drawn from a normal distribution. Then, we generated a Vandermonde matrix ($A$) of time. This is a way of introducing a polynomial least-squares regression with respect to time. The final background flux was calculated by taking $bkg = A \cdot trend$.

We performed an MCMC sampling fit to each parameter. We ran 3 chains with 500 tuning steps and 5000 draws. We discarded the tuning samples in our final modeling best-fits, presented in Table~\ref{tab:table}, along with our selected priors for each parameter we fit. We verified our chains converged via visual inspection and following the diagnostic provided by \cite{Geweke92}.

Our final GP model for stellar variability and planet transits are shown in Figure~\ref{fig:transits}. There is a $\sim 1\%$ flare at \tess\ BKJD 4659.18 that we do not fit. We present zoom-ins on the individual transits in the \tess\ light curve. Per each panel, we present the GP model removed flux (de-trended flux) and the best-fit transit models for each observed transit. Phase-folded transits for \planetknown are presented in Figure~\ref{fig:compare}.

@@

Determining the period of transits has previously been constrained by fitting for orbital periods using MCMC sampling, phase-folding all available transits on the derived transit times and periods, and computing a reduced-$\chi^2$ fit to a flat line \citep{becker19}. Orbital periods that result in a likelihood $> 10^4$ are then ruled out. In our new method, we are fitting for discrete periods in tandem, rather than post-processing from our prior. We take the following approach:

First, we de-trended a localized region (1-day before/after ingress/egress) around the transit of \planete in the \textit{K2} and \tess\ light curves, assuming a constant transit depth and allowing the other parameters to vary. The localized region sped up the computation time for the GP fits. Then, we fit a discrete period model, allowing all other transit parameters to be free. The GP model then sampled over potential discrete periods ranging from $38 - 56$~days. We fit for the additional transit parameters, $\theta$, assuming a constant transit depth between the \textit{K2} and \tess\ observations, $X$. We assumed there is no correlation between the other transit parameters and the period we are fitting for. For each step in our MCMC fit, we compute all possible periods

@@

We ran 5 chains with 500 tuning steps and 5000 draws. Similarly to the transit fits, we discarded the tuning steps before our analysis. We show our results in Figure~\ref{fig:period_e}, where we plot the median period for each tested harmonic against the posterior probability of each harmonic.

@@

Using this method, we find the most likely period of \planete to be 50.748~days. We computed a $\chi^2$-fit to a Gaussian distribution and find the period to be $50.29 \pm 6.62$~days. Even at the lower limit, it is unlikely a transit of \planete will occur in the next orbit of Sector 44. This derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb. If the period of \planete is confirmed to be within the presented range, this would make \allplanets a nearly 4 planet resonant chain.

Independent ground-based monitoring of the system for several days beyond the end of Sector 44 (UT 06 Nov 2021) may be able to observe another transit of the outermost known planet in this system. Using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}, we provide several transit midpoint events observable in Mountain Time [UTC-7], Pacific Time [UTC-8], and Hawaiian Time [UTC-10], given the top 5 most-likely periods for \planete in Table~\ref{tab:planete}.

@@

We compare the differences in transit $R_p/R_\star$ between the \textit{K2} and \tess\ data in Figure~\ref{fig:compare}. We plot the best-fit transit model from \textit{K2} in black, which was generated using parameters from \cite{David2019a} and the \texttt{batman} transit-modeling software \citep{Kreidberg15}. The residuals of the \tess\ light curve with our model (color) and the \textit{K2} model are plotted as well. For \planetknown, the transit $R_p/R_\star$ is shallower in the \tess\ data, while only the measured radius for \planete is larger in the \tess\ data (Figure~\ref{fig:compare}, bottom panel).

\subsection{Radii of \planetknown}

Because \sname is young, it is expected that \allplanets have extended atmospheres due to high levels of stellar irradiation \citep{OwenWu2017} and are slowly evolving as atmospheric mass is lost. Only a tentative mass-loss rate of \planetd has been constrained from observations of the metastable He\,\textsc{I} line, along with non-detections for \planetb and \planetc \citep{Vissapragada21}. As such, we favor that the shallower transit depth for \allplanets is due to the difference in bandpass wavelength coverage between \textit{K2} and \tess, rather than atmospheric evolution. The \textit{K2} bandpass ranges from $\sim 400-900$~nm \citep{Howell2014}, while the \tess\ bandpass ranges from $\sim 600-1000$~nm \citep{Ricker2015}. A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.465\textwidth,trim={0.25cm 0 6.5cm 0}]{figures/folded_compare.pdf}
\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the best-fit parameters from the original \textit{K2} data (black). The residuals between the data and each fit are shown underneath. A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference. The transit depth from the \textit{K2} data is deeper than that from \tess, particularly for \planetb and \planete.} \label{fig:compare}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The ability of a planet to retain hazes/transition hazes is positively correlated with its equilibrium temperature, $T_{eq}$, internal temperature $T_{int}$, and mass, $M_{core}$. \planetknown have calculated $T_{eq}<1000$\,K, assuming an albedo = 0 \citep{David2019a}. Young planets are believed to have high $T_{int}$ due to ongoing gravitational contraction \citep{gu04}. The combination of these two parameters make these planets more likely to have extended atmospheres, while outflow winds lead to the formation of transition hazes \citep{gao20}.

If \planetknown host extended haze-dominated atmospheres, they should have smaller transit radii at mid-IR wavelengths \citep{gao20}. However, without mass estimates for \planetknown, it is difficult to determine if this is the cause of the different transit depths we measured between the \textit{K2} and \tess\ data. While radial velocity mass measurements are challenging for young planets due to the underlying stellar activity, efforts should be taken to try and constrain the planet masses. Another, perhaps more promising approach, would be to derive the planet masses using transit-timing variations \citep[TTVs;][]{agol18}. A full TTV analysis using \textit{K2}, \textit{Spitzer}, and \tess\ transit photometry is presented in Livingston et al. (in prep).

\subsection{Radius of \planete}

We measure a larger transit radius for \planete in the \tess\ data than in the original \textit{K2} data.

If the original transit for \planete was filled-in via spot-crossing events, it is possible we could see signs of such events in this new \tess\ data. \cite{morris17} demonstrated the ability to detect starspot crossing events in short-cadence \textit{Kepler} data. The original \textit{K2} observations for \sname are at the long-cadence observing mode ($\sim 30$-minutes) and therefore are not resolved enough to be able to look for starspot crossings. However, the new \tess\ 20-second and 2-minute data may yield insight into if the anomaly at $t \sim 4648.8$~BKJD is an affect from a starspot crossing event, an overlapping transit of a currently unknown planet, or general noise in the data.

@@

We find the transit depths of \planetknown as observed by \tess\ are shallower than previous \textit{K2} by $1-2\sigma$, with the exception of \planete. We postulate the shallower transit depth could be due to ongoing dusty outflows, that make the transit depth appear shallower. However, measuring the transit depths, as well as measuring the masses of these planets, at longer wavelengths could corroborate this.

@@

\begin{acknowledgments}
We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter, and Chas Beichman and Sarah Blunt for helpful comments on our \tess\ DDT proposal 36. It is a pleasure to thank the Astronomical Data Group at the Flatiron Institute for helpful discussions. ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No. (DGE-1746045).

@@
